### 2021-04-15 papers/SYRCoSE/overview.tex
add TODO for formalization part
add: finmap + relation-algebra

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

Finally, we use yet another feature of \mathcomp --- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009}, 
in order to encode the algebraic hierarchy
of various classes of event structures.

>>>>

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq~system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To encode the algebraic hierarchy of various classes of event structures
we use yet another feature of \mathcomp~--- 
\emph{packed classes}~\cite{Garillot-al:ICTPHOL2009},
which is a design pattern providing multiple inheritance,
maximal sharing of notations and theories,
automated structure inference and it also deals with performance issues.

To facilitate computable semantics, we define a subclass of
finite execution event structures as a sorted sequence of events
combined with finitely supported functions to enhance events with labels,
event predecessors and a functional version of the reads-from relation.

Encoding finitely supported functions is not a trivial endeavor in
a proof assistant and for this use the \finmap~%
\footnote{\url{https://github.com/math-comp/finmap}}
library which is an extension of \mathcomp~providing finite sets and
finite maps on types with a choice opeartor (rather than on finite types).

Since our formalization utilizes relations heavily, we have chosen
to rely on the \relationalgebra~%
\footnote{\url{https://github.com/damien-pous/relation-algebra}}
package which provides a number of tactics to solve goals using
decision procedures for various kinds of relation algebra and
also lattice theory.

% TODO
% The relation-algebra package and lattice theory
% well-foundedness and transitive closure for boolean relations
% identType and how to fight quadratic time complexity
